Exploring Rural Shrink Smart Through Guided Discovery Dashboards

### 2021-12-22 SCCAbstract_SDSS2022-knitr.Rnw
Update SCCAbstract_SDSS2022-knitr.Rnw

\section{Data Description}
{\it Iowa Data} were used to create the SCC dashboard. {\it Iowa Data} is a public data website that collects and updates data on the State of Iowa Government, data are mostly on a town/city level that is not collected in National Data Collection Systems. {\it Iowa Data} website is a unique and detailed database of information about residents, such as liquor sales and school building locations. For the purpose of the Rural Shrink Smart Dashboard, we will collect as much data as possible, such as obtaining fire department and hospital details. These data are collected on all towns that are available. We will use statistical clustering methods will be used to determine the town classifications to help improve the rural towns.

\section{Data Challenges}
{\it Iowa Data} website has an exhaustive and detailed data, but that data collected has missing information. This information can be broken down into two separate types, in which we will call a true missing, a particular service that is missing because the town does not have or offer the service to the community. For example, many small towns do not have a hospital that will only cater to the community, but they will have access to a hospital in a neighboring town. The second type of missing data are when data should be available and are not currently being collected in the data but are available in a different data source. For example, our public school data does not actual represent public schools in bigger cities, suggesting that the closest Elementary school is 20 miles away, which we understood that to be untrue. This type of missing data is very typical in data collection, but could led our research in a poor direction.

>>>>

\section{Data Description}
{\it Iowa Data} were used to create the SCC dashboard. {\it Iowa Data} is a public data website that collects and updates data on the State of Iowa Government, data are mostly on a town/city level that is not collected in National Data Collection Systems. 
\db{{\it Iowa Data} }website is a unique and detailed database of information about residents, such as liquor sales and school building locations. 
\db{For the purpose} of the Rural Shrink Smart Dashboard, we will collect as much data as possible, such as obtaining fire department and hospital details. 
\db{These data} are collected on all towns that are available. We will use statistical clustering methods will be used to determine the town classifications to help improve the rural towns.

\section{Data Challenges}
{\it Iowa Data} website has an exhaustive and detailed data, but that data collected has missing information. 
\db{This} information can be broken down into two separate types, in which we will call a true missing, a particular service that is missing because the town does not have or offer the service to the community. 
\db{For example}, many small towns do not have a hospital that will only cater to the community, but they will have access to a hospital in a neighboring town. 
The second type of missing data are when data should be available and are not currently being collected in the data but are available in a different data source.
\db{For example}, our public school data does not actual represent public schools in bigger cities, suggesting that the closest Elementary school is 20 miles away, which we understood that to be untrue. 
\db{This} type of missing data is very typical in data collection, but could led our research in a poor direction.
